
% JuliaCon proceedings template
\documentclass{juliacon}
\setcounter{page}{1}

% See https://tex.stackexchange.com/questions/550123/underscore-in-doi-in-bibtex-file
\usepackage{underscore}

\begin{document}

\input{header}

\maketitle

\begin{abstract}

    This paper introduces a Julia interface for polyhedral computation libraries such as cdd, lrs, qhull, porta or the parma polyhedra library.
    This notably includes conversion between the representation of a polyhedron as the intersection of half-spaces and hyper-planes and
    its representation as the convex hull of points and rays.
    Moreover, the interface covers the removal of redundant elements from the representations as well as detection of \emph{linearity}, i.e., hyper-planes
    formed by the intersection of half-spaces or lines by the conic hull of rays.
    The package also include a default pure-Julia library that implements the double description method for the representation conversion
    and redundancy removal or linearity detection using a linear programming solver implementing MathOptInterface.
    A polyhedron object is provided in order to abstract away the differences between the libraries and hence allowing to write library-agnostic code.
    This object lazily applies the representation conversion when needed.

\end{abstract}

\section{Introduction}

There are two dual approaches to represent a convex set.
First, it can be described as the Minkowski sum between the convex hull of points
and the conic hull of rays; this is the \emph{Vertex representation} or \emph{V-representation}.
The dual alternative is to obtain the set as the intersection of half-spaces;
this is the \emph{Half-spaces representation} or \emph{h-representation}
It turns out that a convex set admits a finite V-representation if and only if it admits a finite H-represention.
Such convex sets are called \emph{polyhedra} or even \emph{polytopes} when the V-representation contains no ray.

Several algorithms exists to convert a H-representation to a V-representation and vice-versa.
This include the \emph{double description algorithm}~\cite{motzkin1953double,fukuda1996double} implemented in cdd~\cite{fukuda2003cdd},
the reversed search vertex enumeration algorithm~\cite{avis1996reverse} implemented in lrs~\cite{avis1994ac,avis2000revised} and
the quick hull algorithm implemented in qhull~\cite{barber1996quickhull}.
As detailed in \cite{avis1995good}, each of these algorithms outperforms the other two for specific families of polyhedra.
This highlights the importance of implementing algorithm relying on polyhedral computation in a library-agnostic way
so that each user can use the appropriate libary.

\input{bib.tex}

\end{document}

% Inspired by the International Journal of Computer Applications template
